Effects of epidemiological structure on the transient evolution of HIV virulence

### 2017-02-11 ms/S2_appendix.tex
using \section instead of \paragraph in S2

\paragraph*{Supporting Information S2: dynamics of transmission and virulence}

This section presents alternate versions of
the figures from the main text showing time dynamics and summary
statistics in terms of \Lspvl\ and per-year transmission probability
rather than expected progression time to AIDS.

>>>>

\section*{Supporting Information S2: dynamics of transmission and virulence}

This section presents alternate versions of
the figures from the main text showing time dynamics and summary
statistics in terms of expected progression time to AIDS and per-year transmission probability
rather than \Lspvl\.
